### 2021-06-29 src/paper/appendix_data.tex
Minor improvements.
Start on describing the synthetic population in more detail.

We build a synthetic population based on the German microcensus \citep{FDSAeDBUDL2018}.
We only use private households, i.e. exclude living arrangements such as nursing homes as
non-private households vary widely in size and it is very difficult to know which
contacts take place in such households.

We sample households to build our synthetic population of over one million households
keeping for each individual their age, gender, occupation and whether they work on
Saturdays and Sundays.

\begin{itemize}
    \item \textcolor{red}{Describe microcensus campus file and which data we use and for what}
    \item \textcolor{red}{Describe size and sampling of households}
    \item \textcolor{red}{counties are randomly drawn}\comment[id=K]{Find out why!}
    \item \textcolor{red}{how we create the occupation column}
    \item \textcolor{red}{describe how we create the contact model group ids for school,
    work and other}
    \item \textcolor{red}{Describe work contact priority, educ contact priority and
    rapid test compliance parameter and quarantine compliance.}
    \item \textcolor{red}{vaccination rank creation}
\end{itemize}

@@

\begin{figure}[ht]
    \centering
    \caption{Share of Individuals With Rapid Tests}
    \label{fig:share_ever_rapid_test}
    \begin{subfigure}{.55\textwidth}
        \includegraphics[width=0.9 \textwidth]{figures/results/figures/scenario_comparisons/combined_fit/full_share_ever_rapid_test}
    \end{subfigure}%
    \begin{subfigure}{.55\textwidth}
        \includegraphics[width=0.9 \textwidth]{figures/results/figures/scenario_comparisons/combined_fit/full_share_rapid_test_in_last_week}
        %   \caption{Share of Individuals Having Done a Rapid Test in the Last Week}
    \end{subfigure}
    \label{fig:share_rapid_test_last_week}
    \floatfoot{\noindent \textit{Note:} The figure compares the share of individuals who
        have ever done a rapid test or done a rapid test within the last week in our
        simulations to the shares reported in the
        \href{https://projekte.uni-erfurt.de/cosmo2020/web/topic/wissen-verhalten/80-schnelltests/}{COVID-19
        Snapshot Monitoring Survey}. The left panel compares the share of individuals who
        have ever done a rapid test. The right panel compares the share of individuals
        who have done a rapid test within the last seven days in our simulation compared
        to the share reporting to have done at least weekly rapid tests in the last four
        weeks in the COSMO survey. Overall our calibration of rapid tests are slightly
        conservative. The overall share is below that in the study. We fit the share of
        weekly tests quite exactly. However, the study only covers adults while our share
        also includes children who are tested very regularly when attending school.}
\end{figure}

>>>>

We build a synthetic population based on the German microcensus \citep{FDSAeDBUDL2018}.
We only use private households, i.e. exclude living arrangements such as nursing homes as
non-private households vary widely in size and it is very difficult to know which
contacts take place in such living arrangements.

We sample households to build our synthetic population of over one million households
keeping for each individual their age, gender, occupation and whether they work on
Saturdays and Sundays. For each household we draw its county and set the corresponding
federal state.% county is not part of the microcensus campus file
We draw for young children whether they attend a nursery or not \citep{Destatis2020}.

\begin{itemize}
    \item \textcolor{red}{describe how we create the contact model group ids for school,
    work and other}
    \item \textcolor{red}{Describe work contact priority, educ contact priority and
    rapid test compliance parameter and quarantine compliance.}
    \item \textcolor{red}{vaccination rank creation}
\end{itemize}

@@

\begin{figure}[ht]
    \centering
    \caption{Share of Individuals With Rapid Tests}
    \label{fig:share_ever_rapid_test}
    \begin{subfigure}{.55\textwidth}
        \includegraphics[width=0.9 \textwidth]{figures/results/figures/scenario_comparisons/combined_fit/full_share_ever_rapid_test}
        \caption{Share of Individuals That Have Ever Done a Rapid Test}
    \end{subfigure}%
    \begin{subfigure}{.55\textwidth}
        \includegraphics[width=0.9 \textwidth]{figures/results/figures/scenario_comparisons/combined_fit/full_share_rapid_test_in_last_week}
        \caption{Share of Individuals Having Done a Rapid Test in the Last Week}
    \end{subfigure}
    \label{fig:share_rapid_test_last_week}
    \floatfoot{\noindent \textit{Note:} The figure compares the share of individuals who
        have ever done a rapid test or done a rapid test within the last week in our
        simulations to the shares reported in the
        \href{https://projekte.uni-erfurt.de/cosmo2020/web/topic/wissen-verhalten/80-schnelltests/}{COVID-19
        Snapshot Monitoring Survey}. The left panel compares the share of individuals who
        have ever done a rapid test. The right panel compares the share of individuals
        who have done a rapid test within the last seven days in our simulation compared
        to the share reporting to have done at least weekly rapid tests in the last four
        weeks in the COSMO survey. Overall our calibration of rapid tests are slightly
        conservative. The overall share is below that in the study. We fit the share of
        weekly tests quite exactly. However, the study only covers adults while our share
        also includes children who are tested very regularly when attending school.}
\end{figure}
